### 2018-06-05 Maths Notes/Further Pure/FP2/Cheat Sheet/FP2 Cheat Sheet.tex
FP2 Cheat Sheet

\documentclass{article}[18pt]
\usepackage{../../../../format}
\lhead{A Level Maths - FP2}
\usepackage{tabularx}
\begin{document}
\begin{center}
\underline{\huge FP2 Cheat Sheet}
\end{center}
\section{Inequalities}
We can build upon our previous algebraic skills in order to solve more complex inequalities\\
Remember:
\begin{itemize}
\item Don't multiply anything that could be negative - use "squared" things
\item Try to avoid fully expanding where possible
\item Find the critical values (f(x)=0)
\item Sketch the graph to solve
\end{itemize}
\section{Series}
Summations can sometimes be simplified using the method of differences\\
\\
This involves a summation where one term is subtracted from another, often gained from partial fractions. The terms in the middle of the series will then cancel with each other, leaving the summation just the terms at the beginning at the end, by summing these a simpler form can be gained.
\section{Further complex numbers}
Remember that complex fractions can be rationalised by multiplying the top and bottom by the complex conjugate
\subsection{Converting between forms}
When converting from $x+iy$ to a form in r and $\theta$, take the angle from the positive $x$ axis
\subsection{Multiplying and dividing complex numbers}
It is easiest to use the exponential form, then convert if needed
\subsubsection{Multiplying}
$$Z_1Z_2=r_1e^{i\theta_1}\times r_2e^{i\theta_2}=r_1r_2e^{i(\theta_1+\theta_2)}$$
\subsubsection{Dividing}
$$\frac{Z_1}{Z_2}=r_1e^{i\theta_1}\div r_2e^{i\theta_2}=\frac{r+1}{r+2} e^{i(\theta_1-\theta_2)}$$
\subsection{De Moivre's theorem}
This is given on the data sheet and has multiple applications
\subsubsection{Roots of unity}
When solving $z^a=r(\cos(\theta)+i\sin(\theta))$ type questions, remember to first rewrite as:
$$z^a=r(\cos(\theta+2k\pi)+i\sin(\theta+2k\pi))$$
\subsubsection{Powers of cos/sin$\rightarrow$Multiples of $\theta$}
If $z=\cos\theta+i\sin\theta$
$$z+\frac{1}{z}=2\cos\theta$$
$$z-\frac{1}{z}=2i\sin\theta$$
$$z^n+\frac{1}{z^n}=2\cos n\theta$$
$$z^n-\frac{1}{z^n}=2i\sin n\theta$$
\subsubsection{Multiples of $\theta\rightarrow$ Powers of cos/sin}
Whatever the multiple of $\theta$ is, raise $(\cos\theta+i\sin\theta)$ to that power. Use De Moivre's theorem to express this in multiples of $\theta$, and use binomial expansion to express it in terms of powers of $\theta$. Equate the real/imaginary parts, depending on whether it is cos or sin to simplify.

@@

\section{First order differential equations}
\subsection{Solving first order DE using an integrating factor}
Solving $\dfrac{dy}{dx}+P(x)y=Q(x)$\\
\\
IF(Integrating factor) is found by finding $\mathlarger{e^{\int p(x) \ dx}}$ And multiplying the DE by the IF.\\
\\
This will result in the DE being in the form:
$$f(x)\frac{dy}{dx}+f'(x)y$$
This form can then be shortened by integrating:
$$\int f'(x)g(x)+f(x)g'(x) dx=f(x)g(x)+c$$
Integrate both sides then simplify
\section{Second order differential equations}
{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{|X|X|}
\hline
\textbf{Solution to auxiliary equation}&\textbf{General solution}\\
\hline
Two real roots $b^2>4ac$&$Ae^{\alpha x}+Be^{\beta x}$\\
\hline
One real root $b^2=4ac$&$(A+bx)e^{\alpha x}$\\
\hline
Imaginary only root $b^2<4ac$&$y=Ae^{\alpha x}+Be^{-\alpha x}$\\
\hline
Complex root $b^2<4ac$&$y=Ae^{(\beta+\alpha i)x}+Be^{(\beta-\alpha i)x}$\\
\hline
\end{tabularx}}
\subsection{Second ODE=f(x)}
\subsubsection{Standard forms of f(x)}
$f(x)=\lambda$\\
$f(x)=\lambda+\mu x$\\
$f(x)=\lambda+\mu x+\nu x^2$\\
$f(x)=ke^{px}$\\
$f(x)=m\cos\omega x$\\
$f(x)=m\sin\omega x$\\
$f(x)=m\cos\omega x\pm n\sin\omega x$
\\
To solve these find $\frac{dy}{dx}$ and $\frac{d^2y}{dx^2}$ and substitute them into the Second ODE, solving for the unknowns, then add them to the general solution.\\
\\
If there is a clash of terms between the CF and PI, then an alternate PI will be given to you. If in doubt, multiply the standard form through by x, but this will not always work.
\subsection{Boundary conditions}
If boundary conditions are given to you, the values of the unknowns can be found. Substitute the boundary conditions in and rearrange to find unknowns.
\newpage
\subsection{Substitution}
Transformations can be used to simplify differential equations, leaving $\frac{d^2y}{dx^2}$ with no coefficient.\\
Method:\\
\textcolor{red}{\large Find $\frac{dy}{dx}$ in terms of $\frac{dy}{du}$}
$$x=e^u \quad \frac{dx}{du}=e^u \quad \frac{du}{dx}=e^{-u} \quad 
\frac{dy}{dx}=\frac{dy}{du}\times\frac{du}{dx}=\mathbf{e^{-u}\frac{dy}{du}}
$$
\textcolor{red}{\large Find $\frac{d^2y}{dx^2}$ in terms of $\frac{d^2y}{du^2}$ and $\frac{dy}{du}$}\\
\textcolor{red}{Find $\frac{dy}{du}\Big(\frac{dy}{dx}\Big)$ by applying the product rule}
$$\frac{dy}{du}\Big(\frac{dy}{dx}\Big)=-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}$$
\textcolor{red}{Multiply through by $\frac{du}{dx}$ to find the value of $\frac{d^2y}{dx^2}$}
$$\frac{d^2y}{dx^2}=\frac{dy}{du}\Big(\frac{dy}{dx}\Big)\times\frac{du}{dx}$$
$$\frac{d^2y}{dx^2}=e^{-u}\Big(-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}\Big)$$
$$\frac{d^2y}{dx^2}=\mathbf{e^{-2u}\Big(-\frac{dy}{du}+\frac{d^2y}{du^2}\Big)}$$
\textcolor{red}{Then substitute the values for x,$\frac{dy}{dx}$, and $\frac{d^2y}{dx^2}$ into the original equation to simplify it}

>>>>

\documentclass{article}[18pt]
\usepackage{../../../../format}
\lhead{A Level Maths - FP2}
\usepackage{tabularx}
\begin{document}
\begin{center}
\underline{\huge FP2 Cheat Sheet}
\end{center}
\section{Inequalities}
We can build upon our previous algebraic skills in order to solve more complex inequalities\\
Remember:
\begin{itemize}
\item Don't multiply anything that could be negative - use "squared" things
\item Try to avoid fully expanding where possible
\item Find the critical values (f(x)=0)
\item Sketch the graph to solve
\end{itemize}
\section{Series}
Summations can sometimes be simplified using the method of differences\\
\\
This involves a summation where one term is subtracted from another, often gained from partial fractions. The terms in the middle of the series will then cancel with each other, leaving the summation just the terms at the beginning at the end, by summing these a simpler form can be gained.
\section{Further complex numbers}
Remember that complex fractions can be rationalised by multiplying the top and bottom by the complex conjugate
\subsection{Converting between forms}
When converting from $x+iy$ to a form in r and $\theta$, take the angle from the positive $x$ axis
\subsection{Multiplying and dividing complex numbers}
It is easiest to use the exponential form, then convert if needed
\subsubsection{Multiplying}
$$Z_1Z_2=r_1e^{i\theta_1}\times r_2e^{i\theta_2}=r_1r_2e^{i(\theta_1+\theta_2)}$$
\subsubsection{Dividing}
$$\frac{Z_1}{Z_2}=r_1e^{i\theta_1}\div r_2e^{i\theta_2}=\frac{r+1}{r+2} e^{i(\theta_1-\theta_2)}$$
\subsection{De Moivre's theorem}
This is given on the data sheet and has multiple applications
\subsubsection{Roots of unity}
When solving $z^a=r(\cos(\theta)+i\sin(\theta))$ type questions, remember to first rewrite as:
$$z^a=r(\cos(\theta+2k\pi)+i\sin(\theta+2k\pi))$$
\subsubsection{Powers of cos/sin$\rightarrow$Multiples of $\theta$}
If $z=\cos\theta+i\sin\theta$
$$z+\frac{1}{z}=2\cos\theta$$
$$z-\frac{1}{z}=2i\sin\theta$$
$$z^n+\frac{1}{z^n}=2\cos n\theta$$
$$z^n-\frac{1}{z^n}=2i\sin n\theta$$
These can be calculated by using DMs theorem to find $z^{-1} =\frac{1}{z}$ then adding or subtracting
\subsubsection{Multiples of $\theta\rightarrow$ Powers of cos/sin}
Whatever the multiple of $\theta$ is, raise $(\cos\theta+i\sin\theta)$ to that power. Use De Moivre's theorem to express this in multiples of $\theta$, and use binomial expansion to express it in terms of powers of $\theta$. Equate the real/imaginary parts, depending on whether it is cos or sin to simplify.

@@

\section{First order differential equations}
\subsection{Solving first order DE using an integrating factor}
Solving $\dfrac{dy}{dx}+P(x)y=Q(x)$\\
\\
IF(Integrating factor) is found by finding $\mathlarger{e^{\int p(x) \ dx}}$ And multiplying the DE by the IF.\\
\\
This will result in the DE being in the form:
$$f(x)\frac{dy}{dx}+f'(x)y$$
This form can then be shortened by integrating:
$$\int f'(x)g(x)+f(x)g'(x) dx=f(x)g(x)+c$$
Integrate both sides then simplify
\section{Second order differential equations}
{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{|X|X|X|}
\hline
\textbf{Solution to auxiliary equation}&\textbf{General solution}&\textbf{Trig general solution}\\
\hline
Two real roots $b^2>4ac$&$Ae^{\alpha x}+Be^{\beta x}$&\\
\hline
One real root $b^2=4ac$&$(A+bx)e^{\alpha x}$&\\
\hline
Imaginary only root $b^2<4ac$&$Ae^{\alpha x}+Be^{-\alpha x}$&
$p\cos\alpha x+q\sin\alpha x$
\\
\hline
Complex root $b^2<4ac$&$Ae^{(\beta+\alpha i)x}+Be^{(\beta-\alpha i)x}$&
$e^{\beta x}(p\cos\alpha x+q\sin\alpha x)$
\\
\hline
\end{tabularx}}
P=A+B\\
Q=i(A+B)
\subsection{Second ODE=f(x)}
\subsubsection{Standard forms of f(x)}
$f(x)=\lambda$\\
$f(x)=\lambda+\mu x$\\
$f(x)=\lambda+\mu x+\nu x^2$\\
$f(x)=ke^{px}$\\
$f(x)=m\cos\omega x$\\
$f(x)=m\sin\omega x$\\
$f(x)=m\cos\omega x\pm n\sin\omega x$
\\
To solve these find $\frac{dy}{dx}$ and $\frac{d^2y}{dx^2}$ and substitute them into the Second ODE, solving for the unknowns, then add them to the general solution.\\
\\
If there is a clash of terms between the CF and PI, then an alternate PI will be given to you. If in doubt, multiply the standard form through by x, but this will not always work.
\subsection{Boundary conditions}
If boundary conditions are given to you, the values of the unknowns can be found. Substitute the boundary conditions in and rearrange to find unknowns.
\newpage
\subsection{Substitution}
Transformations can be used to simplify differential equations, leaving $\frac{d^2y}{dx^2}$ with no coefficient.\\
Method:\\
\textcolor{red}{\large Find $\frac{dy}{dx}$ in terms of $\frac{dy}{du}$}
$$x=e^u \quad \frac{dx}{du}=e^u \quad \frac{du}{dx}=e^{-u} \quad 
\frac{dy}{dx}=\frac{dy}{du}\times\frac{du}{dx}=\mathbf{e^{-u}\frac{dy}{du}}
$$
\textcolor{red}{\large Find $\frac{d^2y}{dx^2}$ in terms of $\frac{d^2y}{du^2}$ and $\frac{dy}{du}$}\\
\textcolor{red}{Find $\frac{dy}{du}\Big(\frac{dy}{dx}\Big)$ by applying the product rule}
$$\frac{dy}{du}\Big(\frac{dy}{dx}\Big)=-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}$$
\textcolor{red}{Multiply through by $\frac{du}{dx}$ to find the value of $\frac{d^2y}{dx^2}$}
$$\frac{d^2y}{dx^2}=\frac{dy}{du}\Big(\frac{dy}{dx}\Big)\times\frac{du}{dx}$$
$$\frac{d^2y}{dx^2}=e^{-u}\Big(-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}\Big)$$
$$\frac{d^2y}{dx^2}=\mathbf{e^{-2u}\Big(-\frac{dy}{du}+\frac{d^2y}{du^2}\Big)}$$
\textcolor{red}{Then substitute the values for x,$\frac{dy}{dx}$, and $\frac{d^2y}{dx^2}$ into the original equation to simplify it}
